Under-approximation of Reachability in Multivalued Asynchronous Networks

### 2014-03-14 parts/models.tex
continue flattening

\newcommand{\n}[1][h]{n^{#1}}
\newcommand{\m}[1][h]{m^{#1}}

Because we only use classical logic operators, we can compute the PP on any action in $\ov{\PH}$.
For any action $h \in \ov{\PHh}$, this DNF takes the form:
\[\Fop{h} \equiv \bot \qquad \text{or} \qquad
  \Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m_i}} p_{i,j} \right)\]
where $\n \in \sN^*$ and $\forall i \in \segm{1}{\n}, \m_i \in \sN^*$.
The case $\Fop{h} \equiv \bot$ means that the action can never be played
because it is always preempted other actions with higher priorities.
The case $\Fop{h} \not\equiv \bot$, on the other hand,
can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
These $\n$ conjunctions can be translated to as many prioritized cooperative sorts,
thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m_i}} p_{i,j}$
In this second case, we denote, for any $i \in \segm{1}{\n}$:
$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m_i} \}$

>>>>

\newcommand{\n}[1][h]{n^{#1}}
\newcommand{\m}[1][h,i]{m^{#1}}

Because we only use classical logic operators, we can compute the PP on any action in $\ov{\PH}$.
For any action $h \in \ov{\PHh}$, this DNF takes the form:
\[\Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m}} p_{i,j} \right)\]
where $\n \in \sN$ and $\forall i \in \segm{1}{\n}, \m \in \sN^*$.
If $\n = 0$, then $\Fop{h} \equiv \bot$; this means that $h$ can never be played
due to preemptions by other actions with higher priorities.
If $\Fop{h} \not\equiv \bot$, on the other hand, then in this case $\Fop{h}$
can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
These $\n$ conjunctions can be translated to as many prioritized cooperative sorts,
thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m}} p_{i,j}$
In this second case, we denote, for any $i \in \segm{1}{\n}$:
$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m} \}$.

\begin{definition}
  \label{def:flattening}
  If $k \in \sN^*$, we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
  the flattening of the PH with $k$ classes of priorities $\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}$, with:
  \begin{itemize}
    \item $\PHs = \ov{\PHs} \cup \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
    \item $\PHl = \underset{a \in \PHs}{\times} \PHl_{a}$, where
      $\PHl_{a} = \ov{\PHl}_{a}$ if $a \in \ov{\PHs}$; and 
      $\PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$ otherwise.
    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\varsigma}{f^{h,i}_{\varsigma'}} \mid
      h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
      a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
      f^{h,i}_\varsigma , f^{h,i}_{\varsigma'} \in \PHl_{f^{h,i}} \wedge
      \PHget{\varsigma}{a} \neq a_k \wedge \varsigma' = \varsigma \Cap \{ a_k \} \}$;
%      \todo{From here: ...} \PHget{\varsigma'}{a} = a_k \wedge
%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\varsigma'}{b} = \PHget{\varsigma}{b}) \}$;
%      \todo{... can be replaced by: $\varsigma' = \varsigma \Cap \{ a_k \}$}
    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\varsigma}{\target{h}}{\bounce{h}} \mid
      h \in \ov{\PHh} \wedge f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.

    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
      \mid i\in\segm{1}{n} \wedge
      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
      \wedge
      \get{\varsigma}{a^j}\neq a^j_k 
      \wedge \get{\varsigma'}{a^j}=a^j_k
      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
      \forall l\in\segm{1}{n},l\neq j)
      \}$, 
      the set of actions with priority $1$ that update cooperative sorts;

          \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
          f^i_\varsigma\in \PHl_{f^i} \wedge
          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
        \}$,

  \end{itemize}

\end{definition}
